Hydra Battles and Cie

### 2021-09-13 doc/chapter-powers.tex
Alectryon: chapter on addition chains 46% done

\begin{Coqsrc}
Ltac monoid_eq_A A op one E_eq M  :=
match goal with 
| [ |- E_eq  ?X ?Y ] =>
  let tX := model A op one X with
      tY := model A op one Y in
      (change (E_eq (eval M tX) (eval M tY)))
end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Ltac reflection_correct_tac :=
match goal with
[ |- chain_correct ?n ?c ] =>
 split; [try discriminate |
         let A := fresh "A"
         in let op := fresh "op"
         in let one := fresh "one" 
         in let E_eq := fresh "eq" 
         in let M := fresh "M"
         in let x := fresh "x" 
         in  (try unfold c); unfold chain_apply;
           simpl; red; intros  A op one E_eq M x;
           unfold computation_eval;simpl;
           monoid_eq_A A op one E_eq M;
           apply flatten_valid_2;try reflexivity
        ]
end. 
\end{Coqsrc}

@@

\begin{Coqsrc}
Example C87_ok : chain_correct 87 C87.
Proof.
  Time reflection_correct_tac.
\end{Coqsrc}

\begin{Coqanswer}
 Finished transaction in 0.038 secs (0.038u,0.s) (successful)
\end{Coqanswer}

@@

\begin{Coqsrc}
Inductive computation {A:Type}  : Type :=
| Return (a : A)
| Mult (x y : A) (k : A -> computation).

Definition chain := forall A:Type, A -> @computation A.
\end{Coqsrc}

@@

\begin{Coqanswer}
Inductive
computation_R (A B : Type) (R : A -> B -> Type)
  : computation -> computation -> Type :=
 |    computation_R_Return_R : 
       forall (a1 : A) (a2 : B),  R a1 a2 ->
         computation_R A B R (Return a1) (Return a2)
  | computation_R_Mult_R : forall (x1 : A) (x2 : B),
         R x1 x2 ->
          forall (y1 : A) (y2 : B),
            R y1 y2 ->
            forall (k1 : A -> computation)
                   (k2 : B -> computation),
                      (forall (H : A) (H0 : B),
                          R H H0 -> 
                          computation_R A B R (k1 H) (k2 H0)) ->
                       computation_R A  B R 
                          (z <--- x1 times y1; k1 z)
                          (z <--- x2 times y2; k2 z)
\end{Coqanswer}

@@

\begin{Coqsrc}
Definition parametric (c:chain) :=
  forall A B (R: A -> B -> Type) (a:A) (b:B),
   R a b -> computation_R  R (c A a) (c B b).
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition the_exponent_nat (c:chain) : nat :=
 chain_apply c (M:=Natplus) 1%nat.

Definition the_exponent (c:chain) : positive :=
  chain_execute c Pos.add  1%positive.

Compute the_exponent C87.
\end{Coqsrc}

\begin{Coqanswer}
 = 87%positive
     : positive  
\end{Coqanswer}

@@

\begin{Coqsrc}
Definition power_R  (a:A) :=
  fun (x:A)(n:nat) => n <> 0 /\ x == a ^ n.  
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma  power_R_is_a_refinemnt (a:A) :
  forall(gamma : @computation A)
        (gamma_nat : @computation nat),
    computation_R  (power_R a) gamma gamma_nat -> 
     power_R a (computation_eval gamma)
               (computation_eval (M:= Natplus) gamma_nat).    
(* Proof omitted *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma param_correctness_nat :
 forall c:chain, parametric c ->  
               chain_correct_nat (the_exponent_nat c)  c.
(* Proof omitted *)
\end{Coqsrc}

>>>>

\inputsnippets{Addition_Chains/monoidEqTac}

@@

\inputsnippets{Addition_Chains/reflectionCorrectTac}

@@

\inputsnippets{Addition_Chains/reflectionDemo}

@@

\inputsnippets{Addition_Chains/computationDef,
  Addition_Chains/chainDef}

@@

\inputsnippets{Addition_Chains/paramDemo}

@@

\inputsnippets{Addition_Chains/parametricDef}

@@

\inputsnippets{Addition_Chains/theExponent}

@@

\inputsnippets{Addition_Chains/powerR}

@@

\inputsnippets{Addition_Chains/powerRRef}

@@

\inputsnippets{Addition_Chains/paramCorrectnessNat}
